Automatic Identification and Annotation of Parallel Tasks in Structured Programs

### 2018-01-08 docs/ACM/paper.tex
Added stuff to paper.

>>>>

The algorithm to find tasks is illustrated in Figure \ref{fig:alg_main}. It uses
information of two abstract program structures: the \emph{Control Flow Graph (CFG)} and
the \emph{Program Dependence Graph (PDG)}. The key intuition behind
finding potential tasks relies on a concept that we call \emph{Helices}. A \emph{Helix}
is a set of nodes in the PDG that depend on a Strong Connected Component (SCC) but \emph{do not
integrate the SCC}. Strong Connected Components in the Dependence Graph represent statically
detected iteration dependence, so it arises with loops or with recursive patterns (when the Graph is
interprocedural).  \Figure \ref{fig:helix}  shows what represents a \emph{Helix}.
The insight behind \emph{Helices} is that they represent instructions that are deemed
to repeat more than once and, since they do not have a cycle, they can be executed in parallel.

Therefore, the first step in the algorithm to find tasks is to map these \emph{Helices}
into program regions. The algorithm goes through the Dependence Graph looking for \emph{Helices}
and then finds the minimal covering region for each \emph{Helix}. These minimal regions
are later going to be annotated as tasks in the original program, should they fit a cost model.

After finding potential task regions, next is the \emph{expansion} step. We expand the region to a larger 
one as long as two requisites are met:

\begin{enumerate}  
\item Input and output dependencies are never increased;
\item The potential parallelism is never reduced.
\end{enumerate}
